Ch3 process

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
did it! need to make the big runs now.

est.lomax.mles %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, length(samp.sizes)),
         gp.tails.ratio = gp.tail/tru.tails,
         thresh = factor(threshold)) %>%
  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
  geom_point() +
  labs(title = "GP")
  theme_minimal() -> gp.tail

@@

```{r results='hide'}
nreps <- 100
gp.mles.reps <- data.frame(NULL)

@@

  ith.thresh   <- fevd.mles$threshold[i]
  fevd.mles$gp.tail[i] <- pextRemes(ith.fit, ith.thresh, lower.tail = FALSE)

@@

}
save.image(gp.mles.reps, "Ch3_samplesize/testdf.RData")
```

>>>>

est.lomax.mles %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, length(samp.sizes)),
         gp.tails.ratio = gp.tail/tru.tails,
         thresh = factor(threshold)) %>%
  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
  geom_point() +
  labs(title = "GP") +
  theme_minimal() -> gp.tail

@@

```{r results='hide'}
nreps <- 2
gp.mles.reps <- data.frame(NULL)

@@

  ith.thresh   <- ith.mle.df$threshold[i]
  ith.mle.df$gp.tail[i] <- pextRemes(ith.fit, ith.thresh, lower.tail = FALSE)

@@

gp.mles.reps %>% 
  mutate(ks = 1/shape,
         alphas = scale*ks) %>% 
  #dplyr::select(-c(scale, shape)) %>% 
  mutate(est.cdf = lomax.cdf(threshold, alphas, ks),
         tail = 1- est.cdf, 
         mean = lomax.mean(alphas, ks)) -> gp.mles.reps

save(gp.mles.reps, file = "Ch3_samplesize/testdf.RData")
```

Let's see

n.tru.cdfs <- nrow(gp.mles.reps)/length(tru.cdfs$w.cdfs)

gp.mles.reps %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
         tails.ratio = tail/tru.tails,
         thresh = factor(threshold)) %>%
  drop_na(tails.ratio) %>% 
  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.size, y = tails.ratio, color = thresh)) +
  geom_boxplot() +
  labs(title = "Lomax") +
  theme_minimal() -> lomax.tail

gp.mles.reps %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
         gp.tails.ratio = gp.tail/tru.tails,
         thresh = factor(threshold)) %>%
  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
  geom_boxplot() +
  labs(title = "GP") +
  theme_minimal() -> gp.tail
